Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-02 paper/paper.tex
Added stuff for the pipes I implemented

\subsubsection{Feature-space Enrichment}
Stopword removal:
N-grams:
Fix emoticons:
HTML corrections: 
URL replacement:
Spell checking:

\subsubsection{Disambiguation}
Lowercasing:
Stemming:

>>>>

\subsubsection{Feature-space Enrichment}
Stopword removal: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords. Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets. Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.
N-grams:
Fix emoticons:
HTML corrections: 
URL replacement:
Spell checking: Since twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words. We decided that performing a spell check on the tweet might help the classifier work, since then it would only have to process proper English. In order to perform the spell check, we made use of an api that would return suggestions for misspelled words. Along with the suggested correct spellings of words, we were also given a "confidence" level for each suggestion. By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.

\subsubsection{Disambiguation}
Lowercasing:
Stemming: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem. Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not a real word. We believed that by reducing each word in the tweet to a its stem, we would be able to improve the classifying algorithm's ability to classify. In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.
